Childhood exposure to non-persistent endocrine disruptors, glucocorticosteroids, and neurodevelopment: A study based on the parametric g-formula

### 2024-02-07 output/paper/_tables.qmd
Added 2 metabolites in sheet that I forgot about. Modifying tables according to MV v1.

::: {#tbl-pop-desc}
```{r pop-desc}
targets::tar_load("table1", store = store)
table1
```
**Participant characteristics, by cohort and overall (HELIX subcohort; 2013-2016).**
:::

>>>>

::: {#tbl-pop-desc}
```{r pop-desc}
targets::tar_load("table1", store = store)
table1
  # gt::cols_width(
  #   label ~ gt::px(300)
  # ) |>
  # gt::tab_style(
  #   style = gt::cell_text(size = gt::pct(90)),
  #   locations = gt::cells_body(
  #     columns = dplyr::everything()
  #   )
  # )
```
**Participant characteristics, by cohort and overall (HELIX subcohort; 2013-2016).**
:::

### 2024-02-07 output/paper/manuscript.qmd
Added 2 metabolites in sheet that I forgot about. Modifying tables according to MV v1.

format:
  docx:
    reference-doc: reference_document.docx
    citeproc: true
  # pdf:
  #   pdf-engine: lualatex
  #   number-sections: true
  #   toc: false
  #   keep-tex: false
  #   include-in-header:
  #     text: |
  #       \usepackage{lineno}
  #       \usepackage{rotating}
  #       \usepackage{float}
  #       \usepackage{typearea}
  #   include-before-body:
  #     text: |
  #       \linenumbers

@@

is_hpc <- FALSE
store <- ifelse(
  is_hpc, 
  paste0(
    "/PROJECTES/HELIX_OMICS/DATA_PREVIOUS_MIGRATION/",
    "lorenzoF/data/data_paper3/_targets/_targets_res"
  ), 
  "~/mounts/rstudioserver/data/data_paper3/_targets/_targets_res"
)
id_var <- "HelixID"
num_digits_est = 3
num_digits_sig = 2
params_ <- params(is_hpc = is_hpc)
threshold_within_lod <- params_$steps$rq2$preproc_outcome$llodq$threshold_within
threshold_overall_lod <- params_$steps$rq2$preproc_outcome$llodq$threshold_overall
threshold_within_nan <- params_$steps$rq2$preproc_outcome$missings$threshold_within
threshold_overall_nan <- params_$steps$rq2$preproc_outcome$missings$threshold_overall
knn_k <- params_$steps$rq2$preproc_outcome$missings$k
```

>>>>

format:
  docx:
    # reference-doc: reference_document.docx
    page-width: 8.3
    citeproc: true
  # pdf:
  #   pdf-engine: lualatex
  #   number-sections: true
  #   toc: false
  #   keep-tex: false
  #   include-in-header:
  #     text: |
  #       \usepackage{lineno}
  #       \usepackage{rotating}
  #       \usepackage{float}
  #       \usepackage{typearea}
  #   include-before-body:
  #     text: |
  #       \linenumbers

@@

is_hpc <- FALSE
store <- ifelse(
  is_hpc, 
  paste0(
    "/PROJECTES/HELIX_OMICS/DATA_PREVIOUS_MIGRATION/",
    "lorenzoF/data/data_paper3/_targets/_targets_res"
  ), 
  "~/mounts/rstudioserver/data/data_paper3/_targets/_targets_res"
)
id_var <- "HelixID"
num_digits_est = 2
num_digits_sig = 2
params_ <- params(is_hpc = is_hpc)
threshold_within_lod <- params_$steps$rq2$preproc_outcome$llodq$threshold_within
threshold_overall_lod <- params_$steps$rq2$preproc_outcome$llodq$threshold_overall
threshold_within_nan <- params_$steps$rq2$preproc_outcome$missings$threshold_within
threshold_overall_nan <- params_$steps$rq2$preproc_outcome$missings$threshold_overall
knn_k <- params_$steps$rq2$preproc_outcome$missings$k
```
